### 2019-02-28 papers/journal/encoding.tex
Fixed the wrong sequence of the BMC and SMT encoding
Minor Fixes, Final push

In this section we will present the BMC, SMT and QBF based encoding of both the search and the synthesis problem. We will start with the SMT based encoding and later present the contrast with the BMC encoding.

@@

In order to specify the stability condition, we use a combination of enumeration and nondeterminism.
%
Nondeterminism can be viewed as an oracle that guesses a correct $m$-path for a specific $m$ if it exists. 
%
We then use this path as a witness to ensures that stability is maintained for each outgoing molecule $m$ on every edge $E$.
%
\subsubsection{Constraints for stability condition}
%
We use \texttt{NOracle} to guess the required path to encode the stability condition in VTS.
%
A naive implementation is shown in~\ref{eq:reachbmc1} where \texttt{NOracle}$(m, i, j, w)$ represent the presence of a $m$-$path$ from node $i$ to node $j$ of maximum $w$ length.
%there is a edge between $i^{\prime \prime}$ and01
%$(i \neq i^{\prime \prime})$ with $m$ present, and j is $m$-reachable from $i'$ in less than $p-1$ steps.
%
% \begin{align}
%   NOracle (m, i, j, w) = \exists \, path[h1, ..., hn]: \\ 2 \leq |path| \leq  w + 2  \, \land h1 = i \, \land  hn = j \, \land \\ 
%   \bigvee\limits_{k = 1}^{|path|- 1} \bigvee\limits_{q}  E[hk] [hk+1][q][m] 
%   \tag{S1}\label{eq:reach1}
% \end{align}
%The NOracle can be thought of as a disjunction of $m$-path of increment length. 
%
It performs enumeration of every $m$-$path$, $m$-${paths}_i^j$, of at most $w$ length. 
%
Starting with exploring $m$-${paths}_i^j$ of length 1, a direct edge between $i$ and $j$ with molecule $m$ present on it, until every $m$-${paths}_i^j$ of length $w-1$ is explored.
%by performing series of node hops till final node destination j is reached.
%Starting with $m$-${paths}_i^j$ of length 1 which is a direct edge between $i$ and $j$ with molecule $m$ present on the edge or performing series of node hops till final node destination j is reached.

>>>>

In this section we will present the SMT, BMC and QBF based encoding of both the search and the synthesis problem. We will start with the SMT based encoding and later present the contrast with the BMC encoding.

@@

In order to specify the stability condition, we use a combination of enumeration and nondeterminism.
%
Nondeterminism can be viewed as an oracle that guesses a correct $m$-path for a specific $m$ if it exists. 
%
We then use this path as a witness to ensures that stability is maintained for each outgoing molecule $m$ on every edge $E$.
%
\subsubsection{Constraints for stability condition}
%
We use \texttt{NOracle} to represent the required path to encode the stability condition in VTS.
%
A naive implementation is shown in~\ref{eq:reachbmc1} where \texttt{NOracle}$(m, i, j, w)$ represent the presence of a $m$-$path$ from node $i$ to node $j$ of maximum $w$ length.
%there is a edge between $i^{\prime \prime}$ and01
%$(i \neq i^{\prime \prime})$ with $m$ present, and j is $m$-reachable from $i'$ in less than $p-1$ steps.
%
% \begin{align}
%   NOracle (m, i, j, w) = \exists \, path[h1, ..., hn]: \\ 2 \leq |path| \leq  w + 2  \, \land h1 = i \, \land  hn = j \, \land \\ 
%   \bigvee\limits_{k = 1}^{|path|- 1} \bigvee\limits_{q}  E[hk] [hk+1][q][m] 
%   \tag{S1}\label{eq:reach1}
% \end{align}
%The NOracle can be thought of as a disjunction of $m$-path of increment length. 
%
It performs enumeration of every $m$-$path$, $m$-${paths}_i^j$, of at most $w$ length. 
%
Starting with exploring $m$-${paths}_i^j$ of length 1, a direct edge between $i$ and $j$ with molecule $m$ present on it, until every $m$-${paths}_i^j$ of length $w-1$ is explored.
%by performing series of node hops till final node destination j is reached.
%Starting with $m$-${paths}_i^j$ of length 1 which is a direct edge between $i$ and $j$ with molecule $m$ present on the edge or performing series of node hops till final node destination j is reached.
